---
title: "Twitter zzh-gj-jz association"
output:
  pdf_document: default
  html_document: default
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```
```{r packages, include=FALSE}
library(rtweet)
library(ggplot2)
library(tidyverse)  
library(dplyr)
```
In this analysis I will first extract tweets mentioning "#zhangzhehan", "#gongjun" or "#junzhe" and then check the overlap between accounts tweeting about these topics. 

Edit 30/05/22: Added "zhang zhehan" and "gong jun" back to search keywords. 

After playing around a bit I decided to use only hashtags instead of full names to focus on dedicated tweets instead of casual mentions.

First let's get the tweets via Twitter API. Please note that there is a rate limit of up to 18000 tweets per day. Nonetheless, I never manage to get the maximum of 6000 tweets per query for some reason. Therefore this search is limited to the last couple of days.

I will then plot the accounts with the most tweets about these topics.

Note: I previously fltered for tweets in English language, now no more language filter applied.
```{r}
###extract tweets

tweets_extract_plot<-function(words,title){
  tweets<-search_tweets2(words,n = 6000,include_rts = FALSE)
  n_tweets<-nrow(tweets)
  stats<-paste(title,collapse=" ")
  stats<-paste(stats,", n=",n_tweets,"tweets")

  plot<-table(tweets$screen_name)%>% 
    as.data.frame() %>% 
    arrange(desc(Freq)) %>%
    top_n(15) %>% 
    mutate(Var1 = reorder(Var1, Freq)) %>%
    ggplot(aes(x = Var1, y = Freq)) +
    geom_col() +
    xlab(NULL) +
    coord_flip() +
    ggtitle(paste("top accounts tweeting about",stats))
  print(plot)
  return(tweets)
}
zzh_tweets<-tweets_extract_plot(c("#zhangzhehan","zhang zhehan"),"#zhangzhehan")
gj_tweets<-tweets_extract_plot(c("#gongjun","gong jun"),"#gongjun")
jz_tweets<-tweets_extract_plot(c("#junzhe"),"#junzhe")
```

Quick info on which timespan the datasets cover and how many tweets per day
```{r}
#calculate rate of tweets per hour
tweet_stats<-function(data,title){
  print(paste("dataset:",title))
  print(paste("number of tweets:",nrow(data)))
  start<-data[nrow(data),]$created_at
  end<-data[1,]$created_at
  print(paste("start:",start))
  print(paste("end:",end))
  diff = end - start
  print(diff)
  #tweets per day
  tw_p_day<-round(nrow(data)/as.numeric(diff),2)
  print(paste("tweets per day:",tw_p_day))
  return(tw_p_day)
}

st_zzh<-tweet_stats(zzh_tweets,"#zhangzhehan")

st_gj<-tweet_stats(gj_tweets,"#gongjun")

st_jz<-tweet_stats(jz_tweets,"#junzhe")

bargraph<-data.frame(group=c("zhangzhehan","gongjun","junzhe"),tweets_per_day=c(st_zzh,st_gj,st_jz))

ggplot(bargraph,aes(x=group,y=tweets_per_day))+
  geom_col()
```

Next let's make a Venn diagram to see the overlap between accounts tweeting about #junzhe, #zhangzhehan or #gongjun.
I have to use 2 Venn diagram packages because gplots gives me the numbers+intersections but only venneuler lets me make a beautiful diagram with proportional circle areas.

```{r}
###Venn diagram
library(gplots)

x <- list("ZZH" = unique(zzh_tweets$screen_name),
          "JunZhe" = unique(jz_tweets$screen_name),
          "GJ" = unique(gj_tweets$screen_name))
v.table <- venn(x)

length(unique(zzh_tweets$screen_name))
length(unique(jz_tweets$screen_name))
length(unique(gj_tweets$screen_name))

x <- attr(v.table,"intersections")
names_venn<-sapply(seq_along(x), function(i) paste(names(x)[[i]]))
numbers_venn<-lapply(seq_along(x), function(i) length(x[[i]]))
names_venn<-str_replace(names_venn, ":", "&")
names_venn<-str_replace(names_venn, ":", "&")
numbers_venn<-as.numeric(numbers_venn)
names(numbers_venn)<-names_venn


library(venneuler)
v <- venneuler(numbers_venn)
plot(v)
```

This Venn diagram only shows numbers of accounts tweeting about the three hashtags
However I also want to see how many tweets are coming from each section of the Venn diagram.

```{r}
#merge lists of tweets
zzh_tweets$group<-c("#zhangzhehan")
gj_tweets$group<-c("#gongjun")
jz_tweets$group<-c("#junzhe")

tweets_all<-rbind(zzh_tweets,gj_tweets,jz_tweets)
#get tweet counts per user
tw_counts_user<-table(tweets_all$screen_name)%>% 
    as.data.frame() %>% 
    arrange(desc(Freq))
names(tw_counts_user)<-c("user","n_tweets")

#get account names from venn slices
venn_slices <- attr(v.table,"intersections")


#tweet counts for accounts in each venn slice
get_tweet_counts<-function(index,data,tweets_count){
  data<-as.data.frame(data)
  names(data)<-c("user")
  data<-merge(data,tweets_count,by=c("user"))
  tweets_sum<-sum(data$n_tweets)
  data %>% 
    arrange(desc(n_tweets)) %>%
    top_n(15) %>% 
    mutate(user = reorder(user, n_tweets)) %>%
    ggplot(aes(x = user, y = n_tweets)) +
    geom_col() +
    xlab(NULL) +
    coord_flip() +
    ggtitle(paste("top accounts tweeting about",index,", n=",tweets_sum,"tweets"))
  
}

lapply(seq_along(venn_slices), function(i) get_tweet_counts(names(x)[[i]], x[[i]],tw_counts_user))

```


Now I have information on which accounts are also tweeting about the other two hashtags I looked at. Will now add this information to bar plot showing tweet counts per hashtag

```{r}
#extract user names for each slice of venn diagram
#transfer user names and slice association to new data frame
add_venn_slice_info<-function(index,data){
  df_out<-data.frame(data,index)
  names(df_out)<-c("screen_name","venn_slice")
  return(df_out)
}

venn_slice_users<-lapply(seq_along(venn_slices), function(i) add_venn_slice_info(names(x)[[i]], x[[i]]))%>% bind_rows()
tweets_all<-(merge(tweets_all,venn_slice_users,by="screen_name"))

#unique(venn_slice_users$venn_slice)

t<-table(tweets_all$group,tweets_all$venn_slice)
#t

print("percent of ZZH tweets from 'pure' ZZH accounts")
t[3,4] / sum(t[3,1:7])
print("percent of ZZH tweets from GJ-mentioning accounts")
t[3,5] / sum(t[3,1:7])
print("percent of ZZH tweets from CP-related accounts")
(sum(t[3,1:7]) - t[3,4] - t[3,5]) / sum(t[3,1:7])
 
print("percent of GJ tweets from 'pure' GJ accounts")
t[1,1] / sum(t[1,1:7])
print("percent of GJ tweets from ZZH-mentioning accounts")
t[1,5] / sum(t[1,1:7])
print("percent of GJ tweets from CP-related accounts")
(sum(t[1,1:7]) - t[1,1] - t[1,5]) / sum(t[1,1:7])                                      
                                       
ggplot(tweets_all,aes(x=group,fill=venn_slice))+
  geom_bar()+
  scale_fill_manual(values = c("ZZH:JunZhe"="blueviolet", 
            "ZZH:JunZhe:GJ" ="purple",
            "GJ" = "red",
            "ZZH" = "blue",
            "JunZhe" =  "violet",
            "ZZH:GJ" = "yellow",
            "JunZhe:GJ"= "magenta"))+ 
    labs(fill = "account assoc.")
```
Let's also look at tweets over time for all three hashtags
```{r}
#names(tweets_all)
ggplot(tweets_all,aes(x=created_at,fill=factor(group)))+
  geom_histogram()+
  facet_wrap(factor(tweets_all$group),ncol=1)+
  scale_x_datetime(date_breaks = "1 day")+
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+ 
    ggtitle("tweets over time")+ 
  theme(legend.position = "none")
```
Same but this time fill color by venn slice
```{r}
#names(tweets_all)
ggplot(tweets_all,aes(x=created_at,fill=venn_slice))+
  geom_histogram()+
  scale_fill_manual(values = c("ZZH:JunZhe"="blueviolet", 
            "ZZH:JunZhe:GJ" ="purple",
            "GJ" = "red",
            "ZZH" = "blue",
            "JunZhe" =  "violet",
            "ZZH:GJ" = "yellow",
            "JunZhe:GJ"= "magenta"))+
  scale_x_datetime(date_breaks = "1 day")+
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+ 
    labs(fill = "account assoc.")+
    ggtitle("tweets over time")
```



